Two photon coupling to atomic relative motional continuum

### 2020-12-06 two-photon.tex
Avoid Im macro

As shown in Fig.~\ref{f-raman-continuum},
since we only have the two Raman frequencies in the experiment,
the energy of the final state is never higher than that of the initial atomic state
and well below the corresponding trap depth.
Therefore, in order to couple to the continuum,
the final state must belong to a different atomic spin state with lower energy.
For our initial spin state of $\Na(2,2),\Cs(3,3)$,
the only candidate for such state is therefore $\Na(1,1),\Cs(3,3)$,
which is lower in energy by $E_{\mathrm{HF}}\approx1.77~\mathrm{GHz}$.
Due to the conservation of $m_f$, this coupling is forbidden if the tweezer is $\pi$-polarized.
Therefore, such coupling can only be caused by impurity in the tweezer polarization.
Using a previously measured tweezer polarization of $C=0.0545$,
where $\mathbf{C}\equiv\abs{\Im\paren{\mathbf{\varepsilon}\times\mathbf{\varepsilon}^*}}$
and $\mathbf{\varepsilon}$ is the polarization vector,
we estimated the Raman Rabi frequency between the molecular state and the $\Na(1,1),\Cs(3,3)$
ground state to be $\Omega_0\approx2\pi500~\mathrm{Hz}$.
Combining the 4 different pathways in Fig.~\ref{f-raman-continuum}(b-e),
the total scattering expected is,
\begin{align*}
  \Gamma=&\Omega_0^2\sqrt{\frac{2\pi}{\omega_1\omega_2\omega_3}}
           \paren{\sqrt{E_{\mathrm{HF}}}+4\sqrt{E_{\mathrm{HF}}-E_b}+\sqrt{E_{\mathrm{HF}}-2E_b}}\\
  \approx&2\pi\times200~\mathrm{Hz}
\end{align*}
where $E_b$ is the binding energy of the molecule.
The order-of-magnitude agreement between this rough estimate and the observed loss rate
of $2\pi\times800~\mathrm{Hz}$ suggests that this loss mechanism
could potentially explain the loss we observe given the correct tweezer polarization.

>>>>

As shown in Fig.~\ref{f-raman-continuum},
since we only have the two Raman frequencies in the experiment,
the energy of the final state is never higher than that of the initial atomic state
and well below the corresponding trap depth.
Therefore, in order to couple to the continuum,
the final state must belong to a different atomic spin state with lower energy.
For our initial spin state of $\Na(2,2),\Cs(3,3)$,
the only candidate for such state is therefore $\Na(1,1),\Cs(3,3)$,
which is lower in energy by $E_{\mathrm{HF}}\approx1.77~\mathrm{GHz}$.
Due to the conservation of $m_f$, this coupling is forbidden if the tweezer is $\pi$-polarized.
Therefore, such coupling can only be caused by impurity in the tweezer polarization.
Using a previously measured tweezer polarization of $C=0.0545$,
where $\mathbf{C}\equiv\abs{\mathrm{Im}\paren{\mathbf{\varepsilon}\times\mathbf{\varepsilon}^*}}$
and $\mathbf{\varepsilon}$ is the polarization vector,
we estimated the Raman Rabi frequency between the molecular state and the $\Na(1,1),\Cs(3,3)$
ground state to be $\Omega_0\approx2\pi500~\mathrm{Hz}$.
Combining the 4 different pathways in Fig.~\ref{f-raman-continuum}(b-e),
the total scattering expected is,
\begin{align*}
  \Gamma=&\Omega_0^2\sqrt{\frac{2\pi}{\omega_1\omega_2\omega_3}}
           \paren{\sqrt{E_{\mathrm{HF}}}+4\sqrt{E_{\mathrm{HF}}-E_b}+\sqrt{E_{\mathrm{HF}}-2E_b}}\\
  \approx&2\pi\times200~\mathrm{Hz}
\end{align*}
where $E_b$ is the binding energy of the molecule.
The order-of-magnitude agreement between this rough estimate and the observed loss rate
of $2\pi\times800~\mathrm{Hz}$ suggests that this loss mechanism
could potentially explain the loss we observe given the correct tweezer polarization.
